The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-07 paper.tex
update

\Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.
The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\

We find that the simulated gamma-ray\
spectra for all latitudes exhibit a spectral cutoff around energies 400--500 GeV,\
consistent with the observed cutoff energy.\
This is expected since
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) is mainly from\
the scatterings between the high-energy CRe ($\gamma\gtrapprox0.8\times10^{6}$) and optical starlight ($\epsilon \sim 10$ eV),\
and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit $\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy (562.1 GeV) is carried away by the upscattered photons ( $\sim$ 450 GeV ).

@@

  Having successfully reproduced the morphology\
  and spectrum of the \textit{Fermi} bubbles,\
  we now ask whether CRe could also explain\
  the Galactic microwave haze.

>>>>

\Cref{fig__gammaRaySynchtronSpectrum} shows the simulated microwave (left)\
and gamma-ray (right) spectra averaged over the different patches (shown in the legends) of the sky.\
The row from top to bottom shows the microwave (left) and gamma-ray (right) spectra\
with CRe spectral index $2.2, 2.4$ and $2.6$, respectively.\

We find that the simulated gamma-ray spectra are well fitted by\
the CRe spectral index 2.4 (the middle row),\
and display several similar features as observed.

First, the simulated and observed spectra of the \textit{Fermi} bubbles is\
nearly latitude independent, and characterized by a broad bump that roughly peaks around $\sim10$ GeV.\
However, the high-latitude spectrum tends to be slightly dimmer than low-latitude\
probably because the optical intensity in ISRF decays with increasing latitude.

Second, the gamma-ray spectra for all latitudes exhibit a spectral cutoff around energies 400--500 GeV,\
consistent with the observed cutoff energy.\
This is expected since
the upscattered high-energy photons ($\epsilon_{1}\sim450$ GeV) mainly arise from\
the relativistic scatterings between the high-energy CRe ($\gtrapprox 408$ GeV)\
and optical starlight ($\epsilon \sim 10$ eV),\
and therefore \Cref{gamma-min} can be reduced to $\epsilon_{1}\sim\gamma m_{\text{e}}c^2$\
in the Klein--Nishina limit\
$\left(\text{i.e. }\epsilon_{1}\epsilon \gg \left(m_{\text{e}}c^2\right)^2\right)$,\
implying most of the CRe energy is carried away by the upscattered photons.

@@

%  Having successfully reproduced the morphology\
%  and spectrum of the \textit{Fermi} bubbles,\
%  we now ask whether CRe could also explain\
%  the Galactic microwave haze.
